\documentclass[10pt]{article}
\usepackage{cv}
\usepackage[english]{babel}
\usepackage{csquotes}

\cvname{Niels Bik}

\cvpersonalinfo{
    \mailto{hey@nielsbik.nl} | \href{https://www.linkedin.com/in/nielsrowinbik}{linkedin.com/in/nielsrowinbik} | \href{https://www.github.com/nielsrowinbik}{github.com/nielsrowinbik}
}

\begin{document}

\makecvtitle

\section{Work experience}
\label{sec:work}

\cvsubsection{Stuvia}[Product Manager][Remote][2023-present]
\begin{itemize}
    \item Tasked with formalising product management practices and growing the product as Stuvia's first product hire.
\end{itemize}

\cvsubsection{ProRail}[Product Manager][Utrecht, NL][2018-2022]
\begin{itemize}
    \item Led four product teams and revamped the engineering process for \enquote{Donna} (software used for capacity allocation of the Dutch railroad system, with its primary output being the timetable), re-introducing foundational Scrum practices and a focus on delivering working software, resulting in 100\% fewer service interruptions directly following each quarterly release.
    \item Set product vision and strategy for the first time since Donna's launch in 2005. Got stakeholder buy-in for a complete overhaul of the product and started a shift at the strategic level from output to outcome.
    \item Established and rolled out processes and tools to enable a structured approach to identifying and validating problems and their solutions (\enquote{Discovery}), continuing the shift from output to outcome at the tactical and operational level.
    \item Established a hiring procedure and led a team of six product managers after scaling up development efforts for Donna.
    \item Launched an improved (80+\% fewer false positives, unknown amount of fewer false negatives, 50\% faster) conflict-detection module for Donna with accompanying visualisation, vastly improving the quality of the timetable and laying the foundation for important technological advancements for the Dutch rail sector such as Automatic Train Operation (ATO).
\end{itemize}

\cvsubsection{ProRail}[Associate Product Manager (i.a.) (parttime)][Utrecht, NL][2016-2018]
\begin{itemize}
    \item Established a way of working and onboarding procedure as the first hire for the \enquote{ProRail ICT student pool} (programme for students to gain relevant work experience). Increased publicity of the pool by arranging and giving a presentation for all managers in the ICT business unit.
    \item Helped the product manager for ProRail's \enquote{Btd-planner} (used for capacity allocation of 20.000 yearly maintenance activities on the Dutch railroad system) take back control of his Product Backlog as an Assistant Product Manager.
\end{itemize}

\section{Education}
\label{sec:school}

\cvsubsection{Utrecht University}[Master in Business Informatics, entrepreneurial track][Utrecht, NL][2016-2018]
\begin{itemize}
    \item Built a proof-of-concept web application called \enquote{openSEA} accompanying a thesis titled \enquote{Developing a model-driven socio-environmental auditing tool}, building the case for a more open approach to socio-environmental auditing.
    \item Authored and published a paper in which I propose a reference method for applying User Stories and co-authored and published a paper based on the research in my thesis (see \hyperref[sec:pubs]{publications}).
\end{itemize}

\cvsubsection{Utrecht University}[Bachelor's programme in Information Science][Utrecht, NL][2012-2016]
\begin{itemize}
    \item Internship at Planbition (\link{www.planbition.eu}, Nijmegen, NL), during which I researched requirements elicitation techniques and applied the findings to investigate and identify which requirements a new feature in Planbition's software should meet. Produced a thesis titled \enquote{Requirements specification of automated planning systems for employment agencies}.
\end{itemize}

\section{Publications}
\label{sec:pubs}

\begin{itemize}
    \item S. España, N. Bik and S. Overbeek, \enquote{Model-driven engineering support for social and environmental accounting,} \textit{2019 13th International Conference on Research Challenges in Information Science (RCIS)}, 2019, pp. 1-12, doi:\\ 10.1109/RCIS.2019.8877042.
    \item N. Bik, G. Lucassen and S. Brinkkemper, \enquote{A Reference Method for User Story Requirements in Agile Systems Development,} \textit{2017 IEEE 25th International Requirements Engineering Conference Workshops (REW)}, 2017, pp. 292-298, doi: 10.1109/REW.2017.83.
\end{itemize}

\section{Additional information and technical skills}
\label{sec:other}

\begin{itemize}
    \item \textbf{\underline{Visitter}}: Freemium SaaS solution for managing vacation home availability. Originally built for parents' vacation home, but made available publicly at \link{https://visitter.app}. Built using Next.js, PlanetScale, and SendGrid.
    \item \textbf{\underline{Qoffeetime}}: Built and published a coffee timer web app out of a personal need to time coffee brewing recipies and the desire to learn Next.js. Available at \link{https://qoffeetime.app}.
    \item Extensive experience with React and related frameworks, libraries and technologies such as Next.js, Tailwind CSS, Webpack, and Git. Limited experience with other web frameworks such as Vue, Svelte, and Lit.
    \item Basic knowledge of Docker, having used it to self-host several services, and underlying container technology.
\end{itemize}

\end{document}